A complete solution for scattering in a kind of quiver gauge theory

### 2025-04-12 Intermediate report/main.tex
New

\begin{document}
\frame{\titlepage}
\section{Why we need new method?}
\begin{frame}
    \frametitle{Why we need new method?}
    Feynman diagram is a brilliant method without doubt, but it also faces many challenges.
    \begin{itemize}
        \item How to compute high multiplicity amplitudes, like n gluons scattering.
        \item Gauge redundancies bring us many structral complications and non-physical degrees of freedom.
        \item Some symmetries are hidden, like the dual superconformal symmetry for $\mathcal{N}=4$ SYM.
        \item Is the local field theory the most basic discription for physics?
    \end{itemize}
    \includegraphics{Picture1.png}
\end{frame}
\begin{frame}
    \frametitle{From Frynman diagram to On-shell method}
    On-shell here means that all quantities we use are gauge invariant.
    Specifically, there are many ingredients under this frame
    \begin{itemize}
        \item The analytic continuation for S-matrix.
        \item The color-ordered amplitudes.
        \item The BCFW recursion relation.
        \item The spinor helicity discription for amplitudes.
    \end{itemize}
\end{frame}
\section{Preliminary}
\begin{frame}
    \frametitle{A brief introduction to BCFW}
    BCFW recursion relation is a method to compute scattering amplitude recursively, means that you can 
    compute higher point amplitudes from lower point.
    \par
 \begin{itemize}[label=\textbullet]
    \item Ruth Britto
    \item Freddy Cachazo
    \item Bo Feng
    \item Edward Witten
 \end{itemize}

@@

\end{frame}
\begin{frame}
    \frametitle{From real to complex -- Analytic Continuation}
    \textbf{Why is analytic continuation valid?}
\begin{itemize}
  \item Tree level scattering amplitudes are rational functions of Lorentz invariants, such as $\bm{p_{i\mu}p_j^\mu}$, $\bm{p_{i\mu}\epsilon_j^\mu}$.
  \item \textbf{Locality} tells us that any pole of a tree-level amplitude must correspond to a on-shell propagating particle. 
  \item There's only single pole, no branch cuts (logs, square roots, etc) at tree level.
\end{itemize}
    \begin{center}
    \tikz{
      \draw[double equal sign distance, -Implies, line width=1pt] (0,0) -- (0,-1.2);
    }
    \end{center}
\vspace{0.5em}
\centering
\textcolor{red}{Ampltudes can be shifted to complex plane}
\end{frame}

@@

\begin{frame}
\frametitle{Little Group}
    In the context of relativistic QFT, particles are classified according to the unitary irreducible representations of the Poincaré group.

    A crucial concept in this classification is the 
    \begin{tcolorbox}[thickitembox]
        \textbf{Little Group:} The subgroup of Lorentz transformations that leaves a given four-momentum invariant.
    \end{tcolorbox}
    \begin{itemize}
        \item \textbf{Massless Case}\\
        For a massless particle with representative momentum 
        \begin{equation*}
            p^\mu=(E,0,0,E)
        \end{equation*}
        the little group is $SO(2)\simeq U(1)$.\\
        In terms of spinor-helicity variables, the massless momentum can be written as
        \begin{equation*}
            p_{\alpha \dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}
        \end{equation*}
    \end{itemize}
\end{frame}

\begin{frame}
    \begin{itemize}
        \item[] The action of the little group is:
        \begin{equation*}
            \lambda \rightarrow t^{-1}\lambda, \qquad \tilde{\lambda}\rightarrow t\tilde{\lambda}, \qquad t\in\mathbb{C^*} 
        \end{equation*}
        same as 
        \begin{equation*}
            \aket{\lambda}\rightarrow t\aket{\lambda}, \qquad \sket{\lambda}\rightarrow t\sket{\lambda}
        \end{equation*}
        The scattering amplitudes should transform covariantly under little group scaling:
        \begin{equation*}
            \color{red} \mathcal{A}_n(\{\aket{1},\sket{1},h_1\},\ldots\{t_i^{-1}\aket{i},t_i\sket{i},h_i\},\ldots )=t_i^{2h_i}\mathcal{A}_n
        \end{equation*}
        \item \textbf{Massive Case}\\
        It can also be handled in terms of spinor-helicity variable, see also 	arXiv:1709.04891 [hep-th] (Nima Arkani-Hamed, Tzu-Chen Huang, Yu-tin Huang).
    \end{itemize}
\end{frame}

>>>>

\begin{document}
\frame{\titlepage}
\section{Why we need new method?}
\begin{frame}
    \frametitle{Why we need new method?}
    Feynman diagram is a brilliant method without doubt, but it also faces many challenges.
    \begin{itemize}
        \item How to compute high multiplicity amplitudes, like n gluons scattering.
        \item Gauge redundancies bring us many structral complications and non-physical degrees of freedom.
        \item Some symmetries are hidden, like the dual superconformal symmetry for $\mathcal{N}=4$ SYM.
        \item Is the local field theory the most basic discription for physics?
    \end{itemize}
    \includegraphics{Picture1.png}
\end{frame}
\begin{frame}
    \frametitle{From Frynman diagram to On-shell method}
    On-shell here means that all quantities we use are gauge invariant and satisfy the on-shell condition.
    Specifically, there are many ingredients under this frame
    \begin{itemize}
        \item The analytic continuation for S-matrix.
        \item The color-ordered amplitudes.
        \item The BCFW recursion relation.
        \item The spinor helicity discription for amplitudes.
    \end{itemize}
\end{frame}
\section{Preliminary}
\begin{frame}
    \frametitle{A brief introduction to BCFW}
    BCFW recursion relation is a method to compute scattering amplitude recursively, means that you can 
    compute higher point amplitudes from lower point.
    \par
 \begin{itemize}[label=\textbullet]
    \item Ruth Britto
    \item Freddy Cachazo
    \item Bo Feng
    \item Edward Witten
 \end{itemize}

@@

\end{frame}
\begin{frame}
    \frametitle{From real to complex -- Analytic Continuation}
    \textbf{Why can we conduct analytic continuation?}
\begin{itemize}
  \item Tree level scattering amplitudes are rational functions of Lorentz invariants, such as $\bm{p_{i\mu}p_j^\mu}$, $\bm{p_{i\mu}\epsilon_j^\mu}$.
  \item \textbf{Locality} tells us that any pole of a tree-level amplitude must correspond to a on-shell propagating particle. 
  \item There's only single pole, no branch cuts (logs, square roots, etc) at tree level.
\end{itemize}
    \begin{center}
    \tikz{
      \draw[double equal sign distance, -Implies, line width=1pt] (0,0) -- (0,-1.2);
    }
    \end{center}
\vspace{0.5em}
\centering
\textcolor{red}{Ampltudes can be shifted to complex plane}
\end{frame}

@@

\begin{frame}
\frametitle{Spinor-helicity formalism}
    The critical point for Spinor-helicity formalism is that a 4-vector $p_\mu$ in $(\frac{1}{2},\frac{1}{2})$ representation can be equivalently represented by a bispinor in $(\frac{1}{2},0)\bigoplus (0,\frac{1}{2})$ representation.
    Specifically
    \begin{itemize}
        \item $\bm{\text{Massless Case}}$\\
    \begin{equation*}
        p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\begin{pmatrix*} 
            p^0-p^3 & -p^1+ip^2\\
            -p^1-ip^2 & p^0+p^3
        \end{pmatrix*}
    \end{equation*}
    And $p_{\alpha\dot{\alpha}}$ can be decomposed into product of two Weyl spinors
    \begin{equation*}
        p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}[\lambda|
    \end{equation*}
    Here we can find that there is a ambiguity for the definition, the momentum is invariant under the following redefinition
    \begin{equation*}
        \lambda \rightarrow t^{-1}\lambda, \qquad \tilde{\lambda}\rightarrow t\tilde{\lambda}, \qquad t\in\mathbb{C^*} 
    \end{equation*}
    same as 
    \begin{equation*}
        \aket{\lambda}\rightarrow t^-\aket{\lambda}, \qquad \sket{\lambda}\rightarrow t\sket{\lambda}
    \end{equation*}
    \end{itemize}
\end{frame}

\begin{frame}
    \begin{itemize}
        \item[]  This redefinition just matches the $U(1)$ little group transformation.
        \vspace{0.5em}

        The scattering amplitudes should transform covariantly under little group scaling:
        \begin{equation*}
            \color{red} \mathcal{A}_n(\{\aket{1},\sket{1},h_1\},\ldots\{t_i^{-1}\aket{i},t_i\sket{i},h_i\},\ldots )=t_i^{2h_i}\mathcal{A}_n
        \end{equation*}
        \item \textbf{Massive Case}\\
        It can also be handled in terms of spinor-helicity variable, see also 	arXiv:1709.04891 [hep-th] (Nima Arkani-Hamed, Tzu-Chen Huang, Yu-tin Huang).
    \end{itemize}
\end{frame}
